Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2017-12-04 PAPER.tex
comb through for esyntax/typos up until Section 3.3

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{plots/ant_layout.png}
	\caption{The PAPER-64 antenna layout. We use only the $30$ m East/West baselines for the revised analysis in this 
paper (such as baseline 49\_41).}
	\label{fig:ant_layout}
\end{figure}

@@

\noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$ h Mpc$^{-1}$ at $z = 8.4$. The revision of this limit (Kolopanis et al., \textit{in prep}) stems mostly from previously underestimated signal loss and underestimated error bars, both of which we 
address in the following sections.

For our analysis, we use $8$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (P64 uses a slightly different RA 
range of $0$-$8.6$ hours). All power spectrum results are produced for a center frequency of $151$ MHz using a width of $10$ 
MHz ($20$ channels), identical to the analysis in P64. We note that, besides using only $1$ baseline type instead of the $3$ in 
P64, the PAPER-64 dataset that we use in this case study differs from that in P64 mainly by the fringe-rate filter. In P64, the 
applied filter was degraded by widening it in fringe-rate space. This was chosen in order to increase the number of independent 
modes and reduce signal loss, though as we will see this signal loss was still under-estimated. With the development of a new, 
robust method for assessing signal loss, we choose to use the optimal filter in order to maximize sensitivity. This filter is 
computed for a fiducial $30$ m baseline at $150$ MHz, the center frequency in our band. The filter in both the fringe-rate 
domain and time domain is shown in Figure \ref{fig:frp}.

@@

\subsubsection{Signal Loss Methodology} 
\label{sec:siglossmethod}
To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$ 
cm signal visibilities. Here we use the same method used in P64, where mock Gaussian noise visibilities (mock EoR signals) 
are filtered in fringe-rate space to retain only ``sky-like" time-modes. This signal is then added to the data.  \footnote{One 
specific change from P64 is that we add this simulated signal into the analysis pipeline before the final fringe-rate filter is 
applied to the data. Previously, the addition was done after that final fringe-rate filter step.  This change results in an increased 
estimate of signal loss (by a factor of $\sim$$10$), likely due to the use of the fringe-rate filter as a simulator.}

Suppose that $\textbf{e}$ is the injected EoR (at some amplitude level), and $\textbf{x}$ is our data vector. We define $\textbf{r}
$ to be the data plus the EoR signal:

@@

In short, we can summarize a signal loss estimate as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\textbf{x}$ (our detailed computation is described in the next section). We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\textbf{x}$ by the following reasoning.

@@

Using this motivation, the numerator of Equation \eqref{eq:Deriv2} can be mapped to our expression for $P_{\rm out}$, and the denominator to $P_{\rm in}$, where the function $g$ is our OQE power spectrum pipeline. \dcj{Here is the post-hoc justification for this signal loss method.  Except goes back to assumption of equation for g which just \emph{assumes} that there are no cross terms in the estimation of a power spectrum. So we're just kicking the can down the road. }

@@

However, a deeper investigation of these cross-terms reveals that they can contain non-negligible power when $\textbf{R}_{r}$
is taken to be $\textbf{C}_{r}^{-1}$ and
$\textbf{C}_{r}$ is estimated from the data itself.  As shown in \citet{switzer_et_al2015}, 
$\textbf{C}_{r}^{-1}\textbf{x}$ and
$\textbf{C}_{r}^{-1}\textbf{e}$
can become anti-correlated on average. 
This negative cross-term power arises from inverting the covariance matrix
$\textbf{C}_{r}$. 
Intuitively, we can see this by expanding the covariance of $\textbf{r}=\textbf{x}+\textbf{e}$ in the
$|\textbf{x}|\ll|\textbf{e}|$ regime:

@@

The relationship between the input and output power spectra, $P_{\rm in}$ and $P_{\rm out}$, can be thought of as a transfer function 
which, for a sampling of $P_{\rm in}$ and $P_{\rm out}$ provides a mapping from an input power spectrum distribution into an output 
distribution. By viewing data through this signal loss lens, we may then ask the question ``what input power spectrum 
distribution could this (signal-loss affected) data come from?" In the next section, we describe the shape of our signal loss 
transfer function and detail the computation used to translate our power spectrum result into one viewed through a 
signal loss lens. Interpretation of the signal injection results can be framed in multiple ways which result in similar but not identical answers. One such alternative is described in Appendix \ref{sec:Pr_appendix}.
%We showcase two methods... \cc{fill in with some broad statement of why we're showing 2 methods but also state that they yield similar results...}

@@

We now shift our attention towards computing signal loss for the fringe-rate filtered PAPER-64 dataset. While our methodology 
outlined below is independent of weighting scheme, here we demonstrate the computation using inverse covariance weighting 
($\textbf{R} = \textbf{C}^{-1}$), the weighting scheme used in P64 which leads to substantial loss. With this weighting, our 
expressions for $P_{\rm in}$ and $P_{\rm out}$ become (ignoring normalization factors):

@@

In our code, we simulate $20$ realizations of $\p_{\rm eor}$ by bootstrapping over baselines, as explained in Section \ref{sec:Boot}, yielding $P_{\rm in}$ values that range from $\sim$$-10^{13}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ (negative $P_{\rm in}$ is injected when one copy of \textbf{e} in Equation \eqref{eq:Pin} is negative and the other is positive) to $\sim$10$^{13}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$. We also run $40$ total EoR injection levels, resulting in a total of $800$ data points on our $P_{\rm in}$ vs. $P_{\rm out}$ grid. We smooth the 2D distribution using kernel density estimators. Additionally, we have verified that the transfer function is symmetric for negative and positive $P_{\rm in}$'s, and so we fold all the values into positive ones to increase our signal-to-noise.

The result is shown in the left plot of Figure \ref{fig:sigloss_transfercurve}. Bayes' rule then simply instructs us to fix $\phat$ at our measured value $\phat_{x}$, essentially reading Figure \ref{fig:sigloss_transfercurve} horizontally and reinterpreting Equation \eqref{eq:Bayes} as a function of $p( \p_{\rm eor})$. The final result can then be normalized to give $p( \p_{\rm eor} | \phat)$. If $\phat$ itself does not take on a single value but is itself a distribution (for our analysis, this comes from bootstrapping), then one simply repeats the process for every single point on the distribution of $\phat$, before performing the final summation and normalization. In Figure \ref{fig:sigloss_transfercurve}, the peak of our data distribution $
\hat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines. From the left plot (inverse covariance weighting), one can eyeball that a data value of $10^{5} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a 
value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim1000$. Performing a summation and normalization for the entire distribution of $\hat{\textbf{p}}_{x}$ yields a final $P_{\rm in}$ distribution --- the distribution of our data as seen through the signal loss lens. We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve.png}
	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $P_{\rm out}$, as defined by Equations 
\eqref{eq:Pin} and \eqref{eq:sigloss}. Kernel density estimations of the power spectrum transfer functions are shown as colored 
heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The solid black 
diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\hat{\textbf{p}}$, the data 
distribution. From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss 
for power spectrum values above $\sim$$2 \times 10^{4}$ $mK^{2} \, (h^{-1} \, Mpc)^{3}$, whereas the unweighted case does 
not exhibit loss. The peculiar feature of `signal gain' at low injection levels is explained in the text.}
	\label{fig:sigloss_transfercurve}
\end{figure*}

One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{\rm in}$ values it appears that we can have 
signal gain ($P_{\rm out} > P_{in}$). This is unphysical in nature but caused due to the dominating cross-terms involving $\textbf{e}
$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand} once $\textbf{e}$ becomes small. As $\textbf{e}$ increases, we move 
into a regime where $P_{\rm out} \sim P_{in}$, and then eventually into a regime where $P_{\rm out} < P_{in}$ when $\textbf{e}$ is 
large enough to be destroyed if weighting the data using itself. Although we only show figures for one $k$ value, we note that 
the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately).

@@

To conclude this method, we also show power spectrum results for fringe-rate filtered PAPER-64 data before and after signal 
loss correction in Figure \ref{fig:ps2_data}, using inverse covariance weighting. The blue dashed line represents the unweighted 
power spectrum, which is identical in both panels (an important check, as we expect no signal loss for this case). The black and 
gray points are positive and negative power spectrum values plotted with $2\sigma$ error bars. Prior to signal loss correction, it 
is clear that the power spectrum is unfeasible because it is well below the theoretical noise level prediction (solid green curve). 
Post-correction, the power spectrum errors blow up to be higher than both the theory and unweighted power spectrum, a consequence of not being able to characterize covariances well using the time-averaged fringe-rate filtered data (there is less independent information to use). We elaborate on this point in the next section, as well as investigate alternate 
weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-
weighting contaminants with minimizing the loss of EoR.

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{plots/ps2_data_nosigloss.png}
	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (positive (black) and negative (gray) points, 
with $2\sigma$ error bars) before signal loss correction (left) and after (right). The dashed blue line is the unweighted power 
spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on observational 
parameters, whose calculation is detailed in Section \ref{sec:PSSense}.}
	\label{fig:ps2_data}
\end{figure*}

@@

We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e. flattening out part of the 
eigenspectrum) can help minimize signal loss. We experiment with this idea on PAPER-64 data, dialing the number of modes 
down-weighted from zero (which is equivalent to identity-weighting, or the unweighted case) to $21$ (which is full inverse 
covariance weighting of our $21$ channels). The power spectrum results for one $k$ value, both before and after signal loss 
correction, are shown in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
becomes more aggressive (gray curve). In other words, more `weak' (EoR-dominated) fluctuations are being overfit and 
subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post signal loss correction, 
increases with the number of down-weighted modes (black curve). Because our data is fringe-rate filtered, we have less information to characterize the covariance matrix and therefore do a worse job estimating it. Hence, the more modes we use in down-weighting, the greater the error we have in estimating the power spectrum.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop.png}
	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Values 
are shown before (gray) and after (black) signal loss correction as a function of number of eigenmodes of $\hat{\textbf{C}}$ that 
are down-weighted. This regularization knob is tuned from $0$ modes (i.e. unweighted) to $21$ modes (i.e. full inverse 
covariance weighting). Over $\sim3$ orders of magnitude of signal loss results when using inverse covariance weighting. Also 
plotted for comparison are $2\sigma$ power spectrum upper limits for the unweighted case (dashed blue), inverse variance 
weighted case (red), and added-identity case (cyan). All three regularizations shown (black, red, cyan) perform similarly (when 
$\sim$$3$ modes are down-weighted for the black curve). Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
as solid green.}
	\label{fig:sigloss_modeloop}
\end{figure*}

In addition to our thermal noise prediction (green), two additional horizontal lines are shown in Figure \ref{fig:sigloss_modeloop} 
which denote power spectrum values, post-signal loss correction, for two other regularization schemes. We multiply an identity 
matrix element-wise to $\hat{\textbf{C}}$ (i.e. inverse variance weighting, shown in red), and also add an arbitrarily chosen level 
of $\textbf{I}$ to $\hat{\textbf{C}}$ (cyan). We see that all three regularization schemes (black, red, cyan) perform similarly at 
their best (i.e. when $\sim3$-$4$ eigenmodes are down-weighted in the case of the black curve).

@@

Our revised, best to-date PAPER-64 power spectrum (using only one baseline separation type) is shown in Figure 
\ref{fig:ps1_data}. Again, black and gray points correspond to positive and negative power spectrum values respectively, with 
$2\sigma$ errors bars. Also plotted are the unweighted power spectrum upper limit (dashed blue) and theoretical prediction of 
noise (solid green). From this result, we quote a best $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, 
a higher limit than P64 by a factor of $\sim7$ in mK (though we only use one baseline type in our analysis as opposed to $3$). 
\cc{replace with kolopanis limit instead later}

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{plots/ps1_data_reg.png}
	\includegraphics[width=0.4\textwidth]{plots/ps2_data_reg.png}
	\caption{Power spectrum of PAPER-64 using $\hat{\textbf{C}}_{eff}$. Black and gray points correspond to positive and 
negative power spectrum values, respectively, with $2\sigma$ error bars also plotted. The dashed blue line is the unweighted 
power spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on 
observational parameters. This power spectrum result differs from P64 in that it only uses data from one type of baseline ($30$ m 
East/West baselines) instead of three. Major differences from previously published results stem from revisions regarding signal 
loss, bootstrapping, and the theoretical error computation. We quote a best $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at 
$k=0.34$ $h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}.}
	\label{fig:ps1_data}
\end{figure*}

In this section we have shown three simple ways of regularizing $\hat{\textbf{C}}$ to minimize signal loss using PAPER-64 
data. There are many other weighting schemes that we leave for consideration in future work. For example, one could estimate 
$\hat{\textbf{C}}$ using information from different subsets of baselines. For redundant arrays this could mean calculating $
\hat{\textbf{C}}$ from a different but similar baseline type, such as the $\sim30$ m diagonal PAPER baselines (instead of the 
horizontal E/W ones). Alternately, covariances could be estimated from all other baselines except the two being cross-multiplied 
when forming a power spectrum estimate. This method was used in \citet{parsons_et_al2014} in order to avoid suppressing the 
$21$ cm signal, and it's worth noting that the PAPER-32 results are likely safe from the issue of signal loss underestimation 
because of this very reason (however, they are affected by the error estimation issues described in Section \ref{sec:Error}, so 
we also regard those results as suspect and superseded by those of Kolopanis et al., \textit{in prep}.

Another possible way to regularize $\hat{\textbf{C}}$ is to use information from different ranges of LST. For example, one could 
calculate $\hat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the `foreground-
quiet' range used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to 
down-weight. Fundamentally, each of these examples are similar in that they rely on a computation of $\hat{\textbf{C}}$ from 
data that is similar but not exactly the same as the data that is being down-weighted. Ideally this would be effective in down-
weighting shared contaminants yet avoid signal loss from over-fitting EoR modes in the power spectrum dataset itself.

@@

The sensitivity prediction (\citealt{parsons_et_al2012a}, \citealt{pober_et_al2013}) for a power spectral analysis of 
interferometric $21$ cm data, in temperature-units, is:

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{plots/sense_check.png}
	\caption{An updated prediction for the noise-level of PAPER-64 data (black) is shown in comparison to previously 
published sensitivity limits (gray). Both sensitivity analyses plotted assume only one baseline type (an additional factor of $
\sqrt{3}$ for 3 baseline types is needed to match P64 exactly). Major factors that contribute to the discrepancy are $
\Omega_{eff}$, $N_{days}$ and $N_{bls}$, as described in Section \ref{sec:PSSense}, which when combined decreases our 
sensitivity (higher noise floor) by a factor of $\sim5$ in mK$^{2}$.}
	\label{fig:sense_check}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{plots/ant_layout.png}
	\caption{The PAPER-64 antenna layout. We use only the $30$ m East/West baselines for the revised analysis in this 
paper (such as the baseline involving antennas 49 and 41).}
	\label{fig:ant_layout}
\end{figure}

@@

\noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$ h Mpc$^{-1}$ at $z = 8.4$. The revision of this limit (Kolopanis et al., \textit{in prep}) stems from previously underestimated signal loss and underestimated error bars, both of which we 
address in the following sections.

For our analysis, we use $8$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (P64 uses a slightly different RA 
range of $0$-$8.6$ hours). All power spectrum results are produced for a center frequency of $151$ MHz using a width of $10$ 
MHz ($20$ channels), identical to the analysis in P64. We note that, besides using only one baseline type instead of the three in 
P64, the PAPER-64 dataset that we use in this case study differs from that in P64 mainly by the applied fringe-rate filter. In P64, the 
applied filter was degraded by widening it in fringe-rate space. This was chosen in order to increase the number of independent 
modes and reduce signal loss, though as we will explain in the next section, this signal loss was still under-estimated. With the development of a new, 
robust method for assessing signal loss, we choose to use the optimal filter in order to maximize sensitivity. This filter is 
computed for a fiducial $30$ m baseline at $150$ MHz, the center frequency in our band. The filter in both the fringe-rate 
domain and time domain is shown in Figure \ref{fig:frp}.

@@

\subsubsection{Signal Loss Methodology} 
\label{sec:siglossmethod}
To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$ 
cm signal visibilities. Here we use the same method as in P64, where mock Gaussian noise visibilities (mock EoR signals) 
are filtered in fringe-rate space to retain only ``sky-like" time-modes. This signal is then added to the data.  \footnote{One 
specific change from P64 is that we add this simulated signal into the analysis pipeline before the final fringe-rate filter is 
applied to the data. Previously, the addition was done after that final fringe-rate filter step.  This change results in an increased 
estimate of signal loss (by a factor of $\sim$$10$), likely due to the use of the fringe-rate filter as a simulator. However, this pipeline difference, while significant, is not the dominant reason why signal loss was under-estimated in P64 (the dominant reason is explained in the main text).}

Suppose that $\textbf{e}$ is the injected EoR (at some amplitude level), and $\textbf{x}$ is our data. We define $\textbf{r}
$ to be the data plus the EoR signal:

@@

In short, we can summarize a signal loss estimate as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\hat{\textbf{p}}_{x}$ (our detailed computation is described in the next section). We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\hat{\textbf{p}}_{x}$ by the following reasoning.

@@

Using this motivation, the numerator of Equation \eqref{eq:Deriv2} can be mapped to our expression for $P_{\rm out}$ (Equation \eqref{eq:sigloss}), and the denominator to $P_{\rm in}$ (Equation \eqref{eq:Pin}), where the function $g$ is our OQE power spectrum pipeline. \dcj{Here is the post-hoc justification for this signal loss method.  Except goes back to assumption of equation for g which just \emph{assumes} that there are no cross terms in the estimation of a power spectrum. So we're just kicking the can down the road. }

@@

However, a deeper investigation of these cross-terms reveals that they contain non-negligible power (when $\textbf{R}_{r}$
is taken to be $\textbf{C}_{r}^{-1}$ and $\textbf{C}_{r}$ is estimated from the data itself). Therefore, ignoring the cross-terms significantly under-estimates signal loss, and it is this reason that represents the bulk change of our revised analysis compared to P64.

We now explain why the spurious correlations between $\textbf{e}$ and $\textbf{x}$ contain negative power.  As shown in \citet{switzer_et_al2015}, 
$\textbf{C}_{r}^{-1}\textbf{x}$ and
$\textbf{C}_{r}^{-1}\textbf{e}$
can become anti-correlated on average. 
This negative cross-term power arises from inverting the covariance matrix
$\textbf{C}_{r}$. 
Intuitively, we can see this by expanding the covariance of $\textbf{r}=\textbf{x}+\textbf{e}$ in the
$|\textbf{x}|\ll|\textbf{e}|$ regime:

@@

The relationship between the input and output power spectra, $P_{\rm in}$ and $P_{\rm out}$, can be thought of as a transfer function 
which, for a sampling of $P_{\rm in}$ and $P_{\rm out}$ provides a mapping from an input power spectrum distribution into an output 
distribution. By viewing data through this signal loss lens, we may then ask the question ``what input power spectrum 
distribution could this (signal-loss affected) data come from?" In the next section, we describe the shape of our signal loss 
transfer function and detail the computation used to translate our power spectrum result into one viewed through a 
signal loss lens. We note that interpretation of the signal injection results can be framed in multiple ways which yield similar but not identical answers. One alternative to the method described in the next section is described in Appendix \ref{sec:Pr_appendix}.
%We showcase two methods... \cc{fill in with some broad statement of why we're showing 2 methods but also state that they yield similar results...}

@@

We now shift our attention towards computing signal loss for the fringe-rate filtered PAPER-64 dataset. While our methodology 
outlined below is independent of weighting scheme, here we demonstrate the computation using inverse covariance weighting 
($\textbf{R} = \textbf{C}^{-1}$), the weighting scheme used in P64 which leads to substantial loss. With this weighting, our 
expressions for $P_{\rm in}$ and $P_{\rm out}$ become:

@@

In our code, we simulate $20$ realizations of $\p_{\rm eor}$ by bootstrapping over baselines, as explained in Section \ref{sec:Boot}, yielding $P_{\rm in}$ values that range from $\sim$$-10^{13}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ (negative $P_{\rm in}$ is injected when one copy of \textbf{e} in Equation \eqref{eq:Pin} is negative and the other is positive) to $\sim$10$^{13}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$. We also run $40$ total EoR injection levels, resulting in a total of $800$ data points on our $P_{\rm in}$ vs. $P_{\rm out}$ grid. 
%Additionally, we have verified that the transfer function is symmetric for negative and positive $P_{\rm in}$'s, and so we fold all the values into positive ones to increase our signal-to-noise.

We smooth the 2D distribution of $P_{in}$ vs. $P_{out}$ using kernel density estimators. The result, for inverse covariance weighting, is shown in the left plot of Figure \ref{fig:sigloss_transfercurve}. Bayes' rule then simply instructs us to fix $\phat$ at our measured value $\phat_{x}$, essentially reading Figure \ref{fig:sigloss_transfercurve} horizontally and reinterpreting Equation \eqref{eq:Bayes} as a function of $p( \p_{\rm eor})$. The final result can then be normalized to give $p( \p_{\rm eor} | \phat)$. If $\phat$ itself does not take on a single value but is itself a distribution (for our analysis, this comes from bootstrapping), then one simply repeats the process for every single point on the distribution of $\phat$, before performing the final summation and normalization. In Figure \ref{fig:sigloss_transfercurve}, the peak of our data distribution $
\hat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines. From the left plot (inverse covariance weighting), one can eyeball that a data value of $10^{5} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a 
value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim1000$. Performing a summation and normalization for the entire distribution of $\hat{\textbf{p}}_{x}$ yields a final $P_{\rm in}$ distribution --- the distribution of our data as seen through the signal loss lens. We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve.png}
	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $P_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}. Kernel density estimations of the power spectrum transfer functions are shown as colored 
heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The solid black 
diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\hat{\textbf{p}}_{x}$, the data 
distribution. From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss 
for power spectrum values above $\sim$$2 \times 10^{4}$ $mK^{2} \, (h^{-1} \, Mpc)^{3}$, whereas the unweighted case does 
not exhibit loss.}
	\label{fig:sigloss_transfercurve}
\end{figure*}

One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{\rm in}$ values it appears that we can have signal gain ($P_{\rm out} > P_{in}$). \cc{This is a log-plotting effect and is under-construction!}.
%This is unphysical in nature but caused due to the dominating cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand} once $\textbf{e}$ becomes small.

The shape of our signal loss transfer function can be described as follows. At low injection levels, for small $\textbf{e}$, we are dominated by the cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand}. As $\textbf{e}$ increases, we move 
into a regime where $P_{\rm out} \sim P_{in}$, and then eventually into a regime where $P_{\rm out} < P_{in}$ when $\textbf{e}$ is 
large enough to be destroyed if weighting the data using itself. Although we only show figures for one $k$ value, we note that 
the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately).

@@

To conclude this method, we also show power spectrum results for fringe-rate filtered PAPER-64 data before and after signal 
loss estimation in Figure \ref{fig:ps2_data}, using inverse covariance weighting. The blue dashed line represents the unweighted 
power spectrum, which is identical in both panels (an important check, as we expect no signal loss for this case). The black and 
gray points are positive and negative power spectrum values plotted with $2\sigma$ error bars. Prior to signal loss estimation, it 
is clear that the power spectrum is unfeasible because it is well below the theoretical noise level prediction (solid green curve). 
Post-estimation, the power spectrum errors blow up to be higher than both the theory and unweighted power spectrum, a consequence of not being able to characterize covariances well using the time-averaged fringe-rate filtered data (there is less independent information to use). We elaborate on this point in the next section, as well as investigate alternate 
weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants with minimizing the loss of EoR.

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{plots/ps2_data_nosigloss.png}
	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (positive (black) and negative (gray) points, 
with $2\sigma$ error bars) before signal loss estimation (left) and after (right). The dashed blue line is the unweighted power 
spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on observational 
parameters, whose calculation is detailed in Section \ref{sec:PSSense}.}
	\label{fig:ps2_data}
\end{figure*}

@@

We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e. flattening out part of the 
eigenspectrum) can help minimize signal loss. We experiment with this idea on PAPER-64 data, dialing the number of modes 
that are down-weighted from zero (which is equivalent to identity-weighting, or the unweighted case) to $21$ (which is full inverse 
covariance weighting of our $21$ channels). The power spectrum results for one $k$ value, both before and after signal loss 
estimation, are shown in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
becomes more aggressive (gray curve). In other words, more `weak' (EoR-dominated) fluctuations are being overfit and 
subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post signal loss estimation, 
increases with the number of down-weighted modes (black curve). Because our data is fringe-rate filtered, we have less information to characterize the covariance matrix and therefore do a worse job estimating it. Hence, the more modes we use in down-weighting, the greater the error we have in estimating the power spectrum.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop.png}
	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Values 
are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\hat{\textbf{C}}$ that 
are down-weighted. This regularization knob is tuned from $0$ modes (i.e. unweighted) to $21$ modes (i.e. full inverse 
covariance weighting). Over $\sim3$ orders of magnitude of signal loss results when using inverse covariance weighting. Also 
plotted for comparison are $2\sigma$ power spectrum upper limits for the unweighted case (dashed blue), inverse variance 
weighted case (red), and added-identity case (cyan). All three regularizations shown (black, red, cyan) perform similarly (when 
$\sim3$$-4$ modes are down-weighted for the black curve). Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
as solid green.}
	\label{fig:sigloss_modeloop}
\end{figure*}

In addition to our thermal noise prediction (green), two additional horizontal lines are shown in Figure \ref{fig:sigloss_modeloop} 
which denote power spectrum values, post-signal loss estimation, for two other regularization schemes. We multiply an identity 
matrix element-wise to $\hat{\textbf{C}}$ (i.e. inverse variance weighting, shown in red), and also add an arbitrarily chosen level 
of $\textbf{I}$ to $\hat{\textbf{C}}$ (cyan). We see that all three regularization schemes (black, red, cyan) perform similarly at 
their best (i.e. when $\sim3$$-4$ eigenmodes are down-weighted in the case of the black curve).

@@

Our revised, best to-date PAPER-64 power spectrum (using only one baseline separation type) is shown in Figure 
\ref{fig:ps1_data}. Again, black and gray points correspond to positive and negative power spectrum values respectively, with 
$2\sigma$ errors bars. Also plotted are the unweighted power spectrum upper limit (dashed blue) and theoretical prediction of 
noise (solid green). From this result, we quote a best $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, 
a higher limit than P64 by a factor of $\sim7$ in mK (though we only use one baseline type in our analysis as opposed to three). 
\cc{replace with kolopanis limit instead later}

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{plots/ps1_data_reg.png}
	\includegraphics[width=0.4\textwidth]{plots/ps2_data_reg.png}
	\caption{Power spectrum of PAPER-64 using $\hat{\textbf{C}}_{eff}$ (inverse variance weighting). Black and gray points correspond to positive and 
negative power spectrum values, respectively, with $2\sigma$ error bars also plotted. The dashed blue line is the unweighted 
power spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on 
observational parameters. This power spectrum result differs from P64 in that it only uses data from one type of baseline ($30$ m 
East/West baselines) instead of three. Major differences from previously published results stem from revisions regarding signal 
loss, bootstrapping, and the theoretical error computation. From this, we quote a best $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at 
$k=0.34$ $h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}.}
	\label{fig:ps1_data}
\end{figure*}

In this section we have shown three simple ways of regularizing $\hat{\textbf{C}}$ to minimize signal loss using PAPER-64 
data. There are many other weighting schemes that we leave for consideration in future work. For example, one could estimate 
$\hat{\textbf{C}}$ using information from different subsets of baselines. For redundant arrays this could mean calculating $
\hat{\textbf{C}}$ from a different but similar baseline type, such as the $\sim30$ m diagonal PAPER baselines (instead of the 
horizontal E/W ones). Alternately, covariances could be estimated from all other baselines except the two being cross-multiplied 
when forming a power spectrum estimate. This method was used in \citet{parsons_et_al2014} in order to avoid suppressing the 
$21$ cm signal, and it's worth noting that the PAPER-32 results are likely less impacted from the issue of signal loss underestimation 
because of this very reason (however, they are affected by the error estimation issues described in Section \ref{sec:Error}, so 
we also regard those results as suspect and superseded by those of Kolopanis et al., \textit{in prep}).

Another possible way to regularize $\hat{\textbf{C}}$ is to use information from different ranges of LST. For example, one could 
calculate $\hat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the `foreground-quiet' range used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to 
down-weight. Fundamentally, each of these examples are similar in that they rely on a computation of $\hat{\textbf{C}}$ from 
data that is similar but not exactly the same as the data that is being down-weighted. Ideally this would be effective in down-weighting shared contaminants yet avoid signal loss from over-fitting EoR modes in the power spectrum dataset itself.

@@

The sensitivity prediction (\citealt{parsons_et_al2012a}; \citealt{pober_et_al2013}) for a power spectral analysis of 
interferometric $21$ cm data, in temperature-units, is:

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{plots/sense_check.png}
	\caption{An updated prediction for the noise-level of PAPER-64 data (black) is shown in comparison to previously 
published sensitivity limits (gray). Both sensitivity analyses plotted assume only one baseline type (an additional factor of $
\sqrt{3}$ for three baseline types is needed to match P64 exactly). Major factors that contribute to the discrepancy are $
\Omega_{eff}$, $N_{days}$ and $N_{bls}$, as described in Section \ref{sec:PSSense}, which when combined decreases our 
sensitivity (higher noise floor) by a factor of $\sim5$ in mK$^{2}$.}
	\label{fig:sense_check}
\end{figure}
